Verifying Demonstrations

### 2018-02-19 paper/DB-anon-cred.tex
DBS: Adds to security discussion

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge we must choose \(k\) 
logarithmically in the security parameter \(\lambda\) and repeat the protocol 
until the knowledge error is small enough.
This will actually also decrease the success probability of \iac{DBMF} adversary 
in the \ac{DB} step.
The \ac{DBMF} adversary does not know which challenge the verifier will use, 
thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it 
correctly.
The prover will only provide one of the responses: even if the adversary re-runs 
the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) 
will have changed --- which thus yields another \(R_b\) in the end of the 
protocol.
By repeating the protocol we can bring this probability down as much as desired.

The random delay in the \ac{DB} phase is important to prevent distance fraud.
Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
round-trip time without waiting for the challenges.
On the other hand, these delays must not be long enough to allow the \ac{DBMF} 
adversary to buffer the responses from the prover.

Distance hijacking, \ac{DBDH} \dots

>>>>

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge we must choose \(k\) 
logarithmically in the security parameter \(\lambda\) and repeat the protocol 
until the knowledge error is small enough.
This will actually also decrease the success probability of \iac{DBMF} adversary 
in the \ac{DB} step.
The \ac{DBMF} adversary does not know which challenge the verifier will use, 
thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it 
correctly.
The prover will only provide one of the responses: even if the adversary re-runs 
the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) 
will have changed --- which thus yields another \(R_b\) in the end of the 
protocol.
By repeating the protocol we decrease this probability.

The random delay in the \ac{DB} phase is important to prevent distance fraud.
Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
round-trip time without waiting for the challenges.
On the other hand, these delays must not be long enough to allow the \ac{DBMF} 
adversary to buffer the responses from the prover.
However, in the worst case, the \ac{DBMF} adversary will be detected in the 
first round, since he cannot buffer any response from the prover.
After the first round though, the adversary knows \(b\) and can get those 
requests as quickly as possible from the prover.
By repeating the protocol we decrease this probability.

The protocol is also secure against distance hijacking.
This follows from the fact that it is the authenticating bit string that is used 
during the \ac{DB} phase.
